The \dealii{} Library, Version 8.5

### 2017-03-09 8.5/paper.tex
Finish reformatting Section 2, rephrase section about incompatible changes

\subsubsection{incompatible change 1}

High-order Lagrange elements, both continuous \verb!FE_Q! and discontinuous
\verb!FE_DGQ! types, now use the nodal points of the Gauss--Lobatto
quadrature formula as support points, rather than the previous equidistant
ones. For cubic polynomials and higher, the point distribution has thus changed and
thus the entries in solution vectors will look different as compared to the previous version. Note, however,
that using the Gauss--Lobatto points as nodal points results in a much more
stable interpolation, including better iteration counts in most iterative
solvers.

\subsubsection{Other incompatible changes}

No \texttt{long double} instantiations any more

ParameterGUI moved to separate repo

The
\href{https://www.dealii.org/8.5.0/doxygen/deal.II/changes_between_8_4_and_8_5.html}{file
  that lists all changes for this release} (see \cite{changes85})
lists another around 20
incompatible changes, but none of these should in fact be visible in
typical user codes. Some remove previously deprecated classes and
functions, and the majority change internal interfaces that are not
typically used in user codes.

>>>>

The 8.5.0 release includes around 20
\href{https://www.dealii.org/8.5.0/doxygen/deal.II/changes_between_8_4_and_8_5.html}{
incompatible changes}; see \cite{changes85}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions, and the majority change internal
interfaces that are not typically used in user codes. However, a number of
incompatible changes a worth mentioning.
\begin{itemize}
  \item High-order Lagrange elements, both continuous \verb!FE_Q! and
    discontinuous \verb!FE_DGQ! types, now use the nodal points of the
    Gauss--Lobatto quadrature formula as support points, rather than the
    previous equidistant ones. For cubic polynomials and higher, the point
    distribution has thus changed and, consequently, the entries in
    solution vectors will look different as compared to the previous
    version. Note, however, that using the Gauss--Lobatto points as nodal
    points results in a much more stable interpolation, including better
    iteration counts in most iterative solvers.
  \item
    The library does not instantiate template versions with \texttt{long
    double} any more. If you need template versions with \texttt{long
    double} make sure to include the corresponding \texttt{templates.h}
    header file.
  \item
    The \texttt{ParameterGUI} has been moved to a separate repository.
\end{itemize}
